Compositional Certified Resource Bounds\ifshort{\vspace{-.15cm}}{}

### 2014-11-07 paper/main.tex
a comment for the structure
update to structure comment
minor corrections

@@

In the second category, are based on type systems for functional
programs and the potential method of amortized
analysis~\cite{Jost03,HoffmannAH12}.  The first challenge of
imperative programs is already the absence of a fine-grained type system to hook
the analysis on.  Another issue is that the techniques associate
\emph{potential} directly to program variables.  In
imperative programs, this would fail for loops as simple as
\lstinline{for(i=x;i<y;i++)} where $y - i$ decreases, but not $|i|$.
Mutation is yet another challenge.  While functional programs relate
multiple fixed inputs (the typing context) with one output (the
expression typed), imperative programs can change the value of
variables in scope, so the potential of these variables has to be
updated after mutations or, unsound bounds can be derived.
%
\jan{@Quentin: There is a mismatch between the previous two paragraphs.
  In the first one we talk about things that category one techniques
  can't do. In the second one we talk about ``challenges'' for the
  category two. We instead should just say what the state-of-the-art
  can't do. We also have to mention Hofmann/Jost ESOP'06 and Atkey ESOP'10.}

>>>>

% Structure:
%
% 1) Intro
% 2) Overview and Examples
% 3) Cost Semantics for Clight
% 4) Compositional Resource-Bound Analysis
% 5) Automatic Inference via LP Solving
% 6) Auxiliary Variables and User Interaction
% 7) Quantitative Hoare Logic and Soundness Proof
% 8) Experimental Evaluation
% 9) Related Work
% 10) Conclusion

@@

Tools in the second category are based on type systems for functional
programs and on the potential method of amortized
analysis~\cite{Jost03,HoffmannAH12}.  The first challenge of
imperative programs is already the absence of a fine-grained type system to hook
the analysis on.  Another issue is that the techniques associate
\emph{potential} directly to program variables.  In
imperative programs, this would fail for loops as simple as
\lstinline{for(i=x;i<y;i++)} where $y - i$ decreases, but not $|i|$.
Mutation is yet another challenge.  While functional programs relate
multiple fixed inputs (the typing context) with one output (the
expression typed), imperative programs can change the value of
variables in scope, so the potential of these variables has to be
updated after mutations or, unsound bounds can be derived.
%
\jan{@Quentin: There is a mismatch between the previous two paragraphs.
  In the first one we talk about things that category one techniques
  can't do. In the second one we talk about ``challenges'' for the
  category two. We instead should just say what the state-of-the-art
  can't do. We also have to mention Hofmann/Jost ESOP'06 and Atkey ESOP'10.}
